### 2010-08-04 docs/volume_discrepancy/volume_discrepancy.tex
add some more details on the form of the w0 equation that we solve in make_w0, when we have the volume discrepancy term

>>>>

In solving the $w_0$ evolution equation
(Eq.~[\ref{eq:w0constraint_vd}]), we expand the divergence, giving
\begin{equation}
\nablab \cdotb (w_0 \er)  = \overline{S} - \frac{1}{\gammabar p_0} \frac{\partial p_0}{\partial t} - 
w_0 \er  \cdotb \frac{1}{\beta_0} \nablab \beta_0  - \frac{f}{\gammabar p_0} \frac{p_0 - \overline{p_\mathrm{EOS}}}{\Delta t} \enskip .
\end{equation}
Recalling that 
\begin{equation*}
\frac{1}{\gammabar p_0} \frac{\partial p_0}{\partial r} = 
 \frac{1}{\beta_0} \frac{\partial \beta_0}{\partial r}
\end{equation*}
(see Paper~I), and that $\psi \equiv D_0 p_0 / Dt \equiv \partial p_0 / \partial t + 
w_0 \partial p_0 / \partial r$, we have
\begin{equation}
\nablab \cdotb (w_0 \er)  = \overline{S} - \frac{1}{\gammabar p_0} \psi -
 \frac{f}{\gammabar p_0} \frac{p_0 - \overline{p_\mathrm{EOS}}}{\Delta t} \enskip .
\end{equation}
This is the form that is solved in {\tt make\_w0}.
